Proposed Solution

### 2017-01-20 CAV17/secs/intro.tex
from osdi

Configuration errors are one of the most important root causes of
today's software system failures~\cite{xu15systems, yin11anempirical}.
In their empirical study Yin {\em et al.}~\cite{yin11anempirical} report
that about 31\% of system failures were caused by misconfiguration problems and only 20\% were caused by bugs in program code. 
Misconfigurations, in practice, may result in various
system-wide problems, such as security vulnerabilities, 
application crashes, severe disruptions in software
functionality, and incorrect program executions%
~\cite{zhang14encore, yuan11context, xu13do, xu15hey}.

While many efforts have been proposed 
to check, troubleshoot, diagnose, and repair configuration errors%
~\cite{attariyan10automating,
su07autobash, whitaker04configuration},
those tools mainly try to understand {\emph{what}} caused the 
error -- they are still not on a level of
automatic verification tools used for regular program 
verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
detect errors without executing the code.
Two main obstacles why we cannot simply apply the existing automatic 
tools and techniques to verification of configuration files are: 1) a lack
of a specification which would describe properties of configuration files, and 2) a program structure of configuration files -- they
are mainly a sequence of entries assigning some value to system variables. The language in which configuration files are written does 
not adhere to a specific grammar or syntax. In particular, the
entries in configuration files are untyped. Moreover, there are surprisingly few rules specifying constraints on entries and there
is no explicit structure policy for the entries.
Thus, automated verification of configuration 
files would be highly
desirable~\cite{wang04automatic, zhang14encore, xu15systems}.

@@

>>>>

Configuration errors are one of the most important root causes of today's software system failures~\cite{xu15systems, yin11anempirical}.
In their empirical study, Yin {\em et al.}~\cite{yin11anempirical} report that about 31\% of system failures were caused by misconfiguration problems and only 20\% were caused by bugs in program code. 
Misconfigurations, result in various system-wide problems, such as security vulnerabilities, application crashes, severe disruptions in software functionality, and incorrect program executions~\cite{zhang14encore, yuan11context, xu13do, xu15hey}.

While many efforts have been proposed to check, troubleshoot, diagnose, and repair configuration errors~\cite{attariyan10automating,su07autobash, whitaker04configuration},
  those tools mainly post-factum and cannot give the safety guarantees available from powerful static analysis tools in program verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15}.
Existing techniques for program verification do not fit this application domain, as configuration files often lack specifications and structure.
There are rarely formal, or any, specifications on the constraints of the key values.
In the case of MySQL, the canonical specification is a 5240 page reference manual~\cite{mysql-manual15} to describe valid configurations and behavior.
We aim to automatically learn a formal specification the encodes this information by examining a set of example configuration files.

In previous work~\cite{santolucitoCAV}, we used a set of manually verified files by an domain expert order to learn specifications.
This approach is expensive and still prone to error by the expert.
Related work on configuration verification has used machine learning

While the grammar of configuration files tends to be simple (a series of key value pairs with some additional context), the keys and values themselves lack often structure and are untyped plain text.

   1) lack of a specification which would describe properties of configuration files, and 
   2) a program structure of configuration files -- they are mainly a sequence of entries assigning some value to system variables. 
The language in which configuration files are written does not adhere to a specific grammar or syntax. 
In particular, the entries in configuration files are untyped. 
Moreover, there are surprisingly few rules specifying constraints on entries and there is no explicit structure policy for the entries.
Thus, automated verification of configuration files would be highly desirable~\cite{wang04automatic, zhang14encore, xu15systems}.

@@

Our main contributions are as follows:

\item Using a probabilistic logical inference approach to the learning task, which builds a more informative structure than state of the art machine learning algorithms

\item A basic application of graph analysis on the learned model to improve results in a way not available to traditional machine learning approaches

\item An open-source implementation, \app, of this approach applied to a set of 256 real world benchmarks. \app identify XX new misconfigurations errors on YY of these files.
\end{enumerate}
